---
title: "Homework 1"
author: "Michelle Jen"
date: "9/17/2019"
output: html_document
---
```{r}
library(tidyverse)
```

# Problem 1

## code chunk 1

Create a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels”


```{r problem_one}

one_df = tibble(
  sample = rnorm(8),
  vec_logical = sample > 0,
  vec_character = c('a','b','c','d','e','f','g','h'),
  vec_factor = factor(c("big","med","small","big","med","small","big","small"))
)

```

Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}
mean(pull(one_df, sample))

mean(pull(one_df, vec_logical))

mean(pull(one_df, vec_character))

mean(pull(one_df,vec_factor))
```

It works to take the mean of a random sample (mean = -0.4653526) and a logical vector (mean = 0.375). However, it doesn't work to take a mean of a character vector or a factor vector since they're not numeric or logical. 


## code chunk 2

In a second code chunk:

* convert the logical vector to numeric, and multiply the random sample by the result
* convert the logical vector to a factor, and multiply the random sample by the result
* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
log_num = as.numeric(pull(one_df,vec_logical))
product_num = log_num*pull(one_df, sample)

log_fact = as.factor(pull(one_df, vec_logical))
product_fact = log_fact*pull(one_df, sample)

fact_num = as.numeric(log_fact)
product_num_random = fact_num*pull(one_df, sample)

```

For the second bullet, finding the product of the factor vactor and random sample yields the result: ‘*’ not meaningful for factors. This makes sense since the factor vector is not numeric so it doesn't work to take the mean.

# Problem 2

Create a data frame comprised of:

* x: a random sample of size 500 from a standard Normal distribution
* y: a random sample of size 500 from a standard Normal distribution
* A logical vector indicating whether x + y > 1
* A numeric vector created by coercing the above logical vector
* A factor vector created by coercing the above logical vector



