---
title: "Homework 1"
author: "Michelle Jen"
date: "9/17/2019"
output: html_document
---
```{r}
library(tidyverse)
```

# Problem 1

## code chunk 1

Create a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels”


```{r problem_one}

one_df = tibble(
  sample = rnorm(8),
  vec_logical = sample > 0,
  chr_vector = c('a','b','c','d','e','f','g','h'),
  vec_factor = factor(c("big","med","small","big","med","small","big","small"))
)

```

Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}
mean(pull(one_df, sample))

mean(pull(one_df, vec_logical))

mean(pull(one_df, chr_vector))

mean(pull(one_df,vec_factor))
```

It works to take the mean of a random sample and a logical vector. However, it doesn't work to take a mean of a character vector or a factor vector since they're not numeric or logical. 


## code chunk 2

as.numeric function to the logical, character, and factor variables

```{r}
log_num = as.numeric(pull(one_df,vec_logical))
product_log = log_num*pull(one_df, sample)

log

```



# Problem 2

Create a data frame comprised of:

* x: a random sample of size 500 from a standard Normal distribution
* y: a random sample of size 500 from a standard Normal distribution
* A logical vector indicating whether x + y > 1
* A numeric vector created by coercing the above logical vector
* A factor vector created by coercing the above logical vector



