---
title: "Homework 1"
author: "Michelle Jen"
date: "9/19/2019"
output: github_document
---
```{r}
library(tidyverse)
```

# Problem 1
## code chunk 1

Create a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels”

```{r problem_one}
one_df = tibble(
  sample = rnorm(8),
  vec_logical = sample > 0,
  vec_character = c('a','b','c','d','e','f','g','h'),
  vec_factor = factor(c("big","med","small","big","med","small","big","small"))
)
```

Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r means}
mean(pull(one_df, sample))
mean(pull(one_df, vec_logical))
mean(pull(one_df, vec_character))
mean(pull(one_df,vec_factor))
```
It works to take the mean of a random sample and a logical vector. However, it doesn't work to take a mean of a character vector or a factor vector since they're not numeric or logical. 

## code chunk 2

In a second code chunk:

* convert the logical vector to numeric, and multiply the random sample by the result
* convert the logical vector to a factor, and multiply the random sample by the result
* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r problem 2}
log_num = as.numeric(pull(one_df,vec_logical))
product_num = log_num*pull(one_df, sample)

log_fact = as.factor(pull(one_df, vec_logical))
product_fact = log_fact*pull(one_df, sample) 
# ‘*’ not meaningful for factors.#
# This makes sense since the factor vector did not yield a mean.# 

fact_num = as.numeric(log_fact)
product_num_random = fact_num*pull(one_df, sample)
```

# Problem 2

Create a data frame comprised of:

* x: a random sample of size 500 from a standard Normal distribution
* y: a random sample of size 500 from a standard Normal distribution
* A logical vector indicating whether x + y > 1
* A numeric vector created by coercing the above logical vector
* A factor vector created by coercing the above logical vector

```{r}
two_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  log_vector = x + y > 1,
  num_vector = as.numeric(log_vector),
  fact_vector = as.factor(log_vector),
)
```

* the size of the dataset (using nrow and ncol) 
* the mean, median, and standard deviation of x 
* the proportion of cases for which x + y > 1

```{r}
nrow(two_df) # The nrow = 500. #
ncol(two_df) # The ncol = 5. #

mean(pull(two_df, x))
median(pull(two_df, x))
sd(pull(two_df, x))

sum(pull(two_df, log_vector)) / 500
```

Make a scatterplot of y vs x; color points using the logical variable (adding color = ... inside of aes in your ggplot code should help). Make a second and third scatterplot that color points using the numeric and factor variables, respectively, and comment on the color scales.

```{r}
scatterplot_one = ggplot(two_df, aes (x=x, y=y, color = (log_vector))) + geom_point()
print(scatterplot_one + ggtitle("First Scatterplot: Logical Vector")) 
# The red represents when the logical vector is false, that is x + y =< 1. #
# The blue represents when the logical vector is true, that is x + y > 1. #
ggsave("scatterplot_one.pdf")

ggplot(two_df, aes (x=x, y=y, color = (num_vector))) + geom_point() 
# The darker blue represents when the numeric vector is false, that is x + y =<. #
# The lighter blue represents when the numeric factor is true, that is x + y > 1. #
# The scale is continuous since it's a numeric vector but values are either 1 or 0 
# (true or false) so theren't any colors in between. #

ggplot(two_df, aes (x=x, y=y, color = (fact_vector))) + geom_point() 
# The red represents when the factor vector is false, that is x + y =< 1. # 
# The blue represents when the factor vector is true, that is x + y > 1. #
```